The Nature and Orbit of the Ophiuchus Stream

### 2015-01-02 tex/ms.tex
better discussion of sigma_v parameter

Given an orbit, the time of disruption $t_{dis}$, and the velocity dispersion of
the stream $\sigma_v$, {\em galpy} can generate a mock stream using the modeling
framework of \citet{bov14}. Observationally, for a fixed $\sigma_v$, $t_{dis}$
is proportional to the stream's length (i.e., older streams are longer). In
Section~\ref{vlos}, we measured $s=0.4$ km s$^{-1}$ as the velocity dispersion
of the stream. We fix $\sigma_v$ to that value, and find that $t_{dis}\sim170$
Myr provides a good match between the observed and mock streams (see
Figure~\ref{observed_vs_mock_comparison}). A much longer or a much shorter time
of disruption produces a much longer or shorter stream that is not consistent
with observations. This result, and the fact that there was a disk+pericenter
passage 250 Myr ago, strongly suggest that the stream formed about 250 Myr ago
(i.e., that the progenitor was disrupted at that time).

As shown by \citet{sb13}, the velocity dispersion of the stream scales with the 
mass of the progenitor as $\sigma_v \propto M_{dyn}^{1/3}$. In {\em galpy}, the
model used for stream generation was calibrated using a progenitor of mass
$M_{dyn}=2\times10^4$ $M_\sun$ which, after it was disrupted, formed a stream
with a velocity dispersion of $\sigma_v=0.365$ km s$^{-1}$ \citep{bov14}. Using
the above scaling relation, we find that the progenitor of the Ophiuchus stream
had a mass of $M_{dyn}\sim2\times10^4$ $M_\sun$.

>>>>

Given an orbit, the time of disruption $t_{dis}$, and the velocity dispersion of
the progenitor $\sigma_v$, {\em galpy} can generate a mock stream using the modeling
framework of \citet{bov14}. Observationally, for a fixed $\sigma_v$, $t_{dis}$
is proportional to the stream's length (i.e., older streams are longer). In
Section~\ref{vlos}, we measured $s=0.4$ km s$^{-1}$ as the velocity dispersion
of the stream. We find that by setting $\sigma_v$ to the same value, the {\em galpy} mock stream has a velocity dispersion $\tilde{s} \approx 0.4$ km s$^{-1} = s$. We further find that $t_{dis}\sim170$
Myr provides a good match between the observed and mock streams (see
Figure~\ref{observed_vs_mock_comparison}). While we do not perform an exhaustive search of the $(\sigma_v,t_{dis})$ parameter space, very different values of $\sigma_v$ or $t_{dis}$ produce values of $\tilde{s}$ or a total length that are not consistent
with observations. This result, and the fact that there was a disk+pericenter
passage 250 Myr ago, strongly suggest that the stream formed about 250 Myr ago
(i.e., that the progenitor was disrupted at that time).

As shown by \citet{sb13}, the velocity dispersion of the progenitor scales with the 
mass of the progenitor as $\sigma_v \propto M_{dyn}^{1/3}$. In {\em galpy}, the
model used for stream generation was calibrated using a progenitor of mass
$M_{dyn}=2\times10^4$ $M_\sun$. The stream formed by the tidal disruption of this progenitor could be modeled with $\sigma_v=0.365$ km s$^{-1}$ \citep{bov14}. Using
the above scaling relation and $\sigma_v = 0.4$ km s$^{-1}$, we find that the progenitor of the Ophiuchus stream
had a mass of $M_{dyn}\sim2\times10^4$ $M_\sun$.
